% LaTeX file for resume 
% This file uses the resume document class (res.cls)

\documentclass{res} 
\usepackage[margin=0.63in]{geometry}
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
\usepackage[english]{babel}
%\setlength{\textheight}{11in} % increase text height to fit on 1-page 
%\setlength{\textheight}{9.5in} % increase text height to fit on 1-page 
\setlength{\textheight}{10.24in} % increase text height to fit on 1-page 
\setlength{\textwidth}{6.24in}
%\addtolength{\topmargin}{-0.5in}
%\addtolength{\oddsidemargin}{-0.2in}
%\addtolength{\evensidemargin}{-.875in}
\begin{document} 
\name{Matthew Daugherty, EIT\\ mattd@daughertyengr.com\\[12pt]}     % the \\[12pt] adds a blank
				        % line after name      

\address{\bf  PRESENT ADDRESS\\2306 Carnation Ct.\\College Station, Tx 77840\\(806) 886-7213}
\address{\bf PERMANENT ADDRESS \\ 12451 Co Rd D 1/2\\Pampa, Tx 79065\\(806) 486-7213}
                                  
\begin{resume}
%\hrule

\section{JOB OBJECTIVE}          
Seeking: Full Time Mechanical Engineering Position in Pursuit of PE
 
\section{EDUCATION}  
	Texas A\&M University, College Station, Tx \\
	Masters of Science, Mechanical Engineering, May 2014 \\
	G.P.A. 3.0/4.0

	Texas A\&M University, College Station, Tx \\
	Bachelor of Science, Mechanical Engineering, May 2011 \\
	G.P.A. 3.3/4.0
 
\section{TECHNICAL PORTFOLIO}
    https://www.daughertyengr.com

\section{EXPERIENCE}
   \vspace{-0.1in}	
   \begin{tabbing}
   \hspace{2.5in}\= \hspace{2.6in}\= \kill % set up two tab positions
   {\bf Mechanical Engineer} \>Peterbilt     \>February 2016-Present\\
    %{\bf }                    \>(HWI)\\
    \>Denton, Tx
   %\end{tabbing}\vspace{-20pt}      % suppress blank line after tabbing
   \end{tabbing}\vspace{-10pt}      % suppress blank line after tabbing
    \begin{itemize}
        \item Request for Engineering Information (Feb 16-Aug 16) - Answered questions over drivelines, frame rails, fifth wheels, fuel tanks, arctic heaters, and sleeper heaters.\\ \vspace{-15pt}
        \item Future Powertrain (Aug 16-Present) - Designed exhaust components installations, compiled and enforced standards. Traveled to support builds. % \vspace{-15pt}
    \end{itemize}

   \begin{tabbing}
   \hspace{2.5in}\= \hspace{2.6in}\= \kill % set up two tab positions
   {\bf NOC Engineer} \>WPEngine     \>March 2015-February 2016\\
    %{\bf }                    \>(HWI)\\
    \>Austin, Tx
   \end{tabbing}\vspace{-20pt}      % suppress blank line after tabbing
   Monitored servers and reacted to problems. Developed tools to streamline solutions to common problems. 

  \begin{tabbing}
   \hspace{2.5in}\= \hspace{2.6in}\= \kill % set up two tab positions
    {\bf Hydraulic Engineer} \>Hydraulic Works Inc.     \>June 2014-January 2015\\
    %{\bf }                    \>(HWI)\\
    \>College Station, Tx
   \end{tabbing}\vspace{-20pt}      % suppress blank line after tabbing
   %Designed/troubleshot hydraulic/electrical systems, rebuilt hydraulic motors/pumps/valves. Built computers and was in house IT.
   Designed, troubleshot, and rebuilt hydraulic and electrical systems and components. Built company computers. Performed internal technical support.

   \begin{tabbing}
   \hspace{2.5in}\= \hspace{2.6in}\= \kill % set up two tab positions
    {\bf Graduate Assistant Researcher} \>Riverside Energy Efficiency Laboratory     \>June 2011-June 2014\\
    %{\bf (GAR)}                    \>(REEL)\\	\>College Station, Tx
    	\>College Station, Tx
   \end{tabbing}\vspace{-20pt}      % suppress blank line after tabbing
   	Experimental Technician. Performed research for developing an industry standard. Coordinated with industry businesses, professional organizations, and technical committees in development of an industry standard. Research and development with clients. Designed and built testing facility for an industry organization.
%   \begin{tabbing}
%   \hspace{2.5in}\= \hspace{2.6in}\= \kill % set up two tab positions
%    {\bf Server Administrator} \>Self-Employed \> May 2009-Present\\
%                          \>Pampa, Tx
%   \end{tabbing}\vspace{-20pt}
%   	Ran production website servers for four commercial entities. Some custom server side services were implemented.
   \begin{tabbing}
   \hspace{2.5in}\= \hspace{2.6in}\= \kill % set up two tab positions
    {\bf Ranch Hand} \>William E. Gething \> May 2004-August 2010 \\
                          \>Pampa, Tx
   \end{tabbing}\vspace{-20pt}
   Mechanic, equipment operator, and metal fabricator\\
   Rebuilt a 1949 International TD-6

\newpage

\section{SKILLS}          
	Proficient in: Creo, Solidworks, \LaTeX{}, HTML, CSS, MatLab, LabView, Bash, BSD, Linux Administration, Python, Radio Frequency, Microcontroller Boards, Control Systems, and Instrumentation.\\
    Familiar with: Basic Sheet Metal, Metal Working (Shield Metal Arc, Oxy-Acetylene, and Plasma Torch), Machining (Mill and Lathe), Woodworking, and Circuit Design.

\section{COURSEWORK}
	Directed Studies, Fluid Mechanics, Advanced Engineering Thermodynamics, Automotive Engineering, and Internal Combustion Engines.

%\section{PROFESSIONAL ORGANIZATIONS}
%	ASHREA member since June 2012\\
%	ASME member since August 2011

\section{ACHIEVEMENTS AND ACTIVITIES}
%\section{LEADERSHIP ACTIVITIES}
    %EIT (Engineer In Training) - License Number 51069\\
	TAMULUG (Texas A\&M Unix and Linux User Group) - President (May 2010-Dec 2011)\\
	Pi Tau Sigma - Public Relations Chair (May 2010-May 2011)\\
	Texas Linux Fest - Volunteer 2010-2012\\
    EAA (Experimental Aircraft Association) - Member\\
    ARRL (Amateur Radio Relay League) - Amateur Radio Operator Extra Class: KF5RHG 

%\section{HONORS AND AWARDS}           
%	Pi Tau Sigma member
    \begin{center}
        For updated resume visit:\\
        http://www.daughertyengr.com/resume.pdf
    \end{center}
\end{resume}
\end{document}
